### 2019-09-01 paper/paper.tex
Change to lower/upper.

\section*{ABSTRACT}
%
Previously, we introduced a method of optimizing four primary geometric
parameters of a bicycle's design to maximize its lateral handling qualities.
Here we expand that method to optimize over all of the geometric and inertial
parameters in the linear Whipple-Carvallo bicycle model. To ensure physically
realizable bicycle designs we include 7 equality constraints, 21 inequality
constraints, and maximal and minimal bounds on each free optimization
parameter. This improves over the prior work by expanding the search space with
many more parameters and the guarantee of physical realizability. We present
four bicycle designs discovered by the optimization procedure that have optimal
later handling qualities. The bicycles are similar in design to familiar
bicycle designs but are not generally self-stable and exhibit unusual
characteristics such as large positive and negative trail, large size relative
to the rider, and minimal steering inertia. The method is a useful tool for
generating atypical bicycle designs that exhibit desired dynamical qualities
and could be broadly applied to other vehicle designs.
%
\begin{keywords}
  bicycle,
  dynamics,
  handling qualities,
  control,
  optimization,
  design
\end{keywords}

>>>>

\section*{ABSTRACT}
%
Previously, we introduced a method of optimizing four primary geometric
parameters of a bicycle's design to maximize its lateral handling qualities.
Here we expand that method to optimize over all of the geometric and inertial
parameters in the linear Whipple-Carvallo bicycle model. To ensure physically
realizable bicycle designs we include 7 equality constraints, 21 inequality
constraints, and lower and upper bounds on each free optimization
parameter. This improves over the prior work by expanding the search space with
many more parameters and the guarantee of physical realizability. We present
four bicycle designs discovered by the optimization procedure that have optimal
later handling qualities. The bicycles are similar in design to familiar
bicycle designs but are not generally self-stable and exhibit unusual
characteristics such as large positive and negative trail, large size relative
to the rider, and minimal steering inertia. The method is a useful tool for
generating atypical bicycle designs that exhibit desired dynamical qualities
and could be broadly applied to other vehicle designs.
%
\begin{keywords}
  bicycle,
  dynamics,
  handling qualities,
  control,
  optimization,
  design
\end{keywords}
